Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-29 paper.tex
Use \textins* vs \textins.
Some uses of \textins were technically supposed to be \textins*

\epigraph{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.%
}{Thomas Jefferson~\cite{barlow:wine}}

@@

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed to
continue to learn more about God's creation without being bound by their financial status.
The Bible encourages one to pursue knowledge. Proverbs 1:5 reads,
\textquote[][.]{%
  \textins{l}et the wise hear and increase in learning, and the one who
  understands obtain guidance%
}
One's ability to live out this verse should not be artificially hindered by financial
station. Just as how someone can go to the library and checkout any book that tickles
their fancy, they should be freely able to learn from the ongoing research of our world.
Of course one should recognize that not all information is safe or helpful to be freely
available on the internet, but that is a topic for a later section.

@@

In the same vein as a VPN is Tor. Tor is a service that allows users to browse the
internet without anyone but themselves knowing both the source and destination of a
connection. Unlike a VPN, there is no central company that can see who is connecting to
what destination; the only person who knows that is the one using the service. The Tor
Project writes, \textcquote{tor:about}[.]{%
  \textins{t}he goal of onion routing was to have a way to use the internet with
  as much privacy as possible, and the idea was to route traffic through
  multiple servers and encrypt it each step of the way%
} Tor not only provides privacy, it gives users total anonymity. Similar to
using a VPN, connecting to the Tor network before browsing the internet makes it
near impossible for observers to see what sites someone is accessing and for the
site to see where the request is coming from.  The potential applications for
near-perfect anonymity on the internet are innumerable. Those living under
oppressive governments can bypass censorship to reach the truth and Christians
can anonymously access the Bible online in restrictive countries, just to name a
few.

@@

\subsubsection{Malware}
The intersection of trust and computing is not a new topic.
\citeauthor{thompson:trust}, the creator of the Unix operating system, made this
the topic of his Turing Award lecture. In his lecture, he poses the question,
\textcquote[761]{thompson:trust}[.]{%
  to what extent should one trust a statement that
  a program is free of Trojan Horses? Perhaps it is more important to trust the
  people who wrote the software%
} With piracy, however, we add an additional actor in this chain of trust.
\citeauthor{thompson:trust} focuses solely on the developer-to-user relationship
of trust, with the assumption of an open-source project.
\citeauthor{thompson:trust}, thus, comments on how
\textcquote[763]{thompson:trust}{%
  \textins{s}uch blatant code would not go undetected for long. Even the most
  casual perusal of the source of the C compiler would raise suspicions%
} When piracy is the method of distribution, however, the assumption of
equality between the source code and the delivered software does not hold. The
pirated software may have been tampered with, and the user has no simple way to
detect changes in the file(s) without doing some (often) complicated forensic
work. Although anti-malware tools may mitigate these issues, the problem of
trust still holds, and the anti-malware tools are not perfect. The character of
the seeder must be questioned, and it already stands on shaky ground if the
legality of their actions speaks for their moral compass and trustworthiness.

>>>>

\epigraph{%
  \textins*{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.%
}{Thomas Jefferson~\cite{barlow:wine}}

@@

Take the restricted access to academic journal articles, for instance. Many academic
journals require all readers to pay not an insignificant sum to access research articles
that could contain insight that is valuable to the human race as a whole. Because of the
high cost of entry, certain groups are automatically excluded from reading and building
upon the research that has already been done. \citeauthor{barlow:wine} puts the situation
eloquently in \citetitle{barlow:wine} when he says, \textcquote{barlow:wine}[.]{%
  I am not comfortable with a model which will restrict inquiry to the wealthy%
}
In the case of academic journal articles, why shouldn't anyone be able to better
themselves by consuming quality research articles? All humans should be allowed to
continue to learn more about God's creation without being bound by their financial status.
The Bible encourages one to pursue knowledge. Proverbs 1:5 reads,
\textquote[][.]{%
  \textins*{l}et the wise hear and increase in learning, and the one who
  understands obtain guidance%
}
One's ability to live out this verse should not be artificially hindered by financial
station. Just as how someone can go to the library and checkout any book that tickles
their fancy, they should be freely able to learn from the ongoing research of our world.
Of course one should recognize that not all information is safe or helpful to be freely
available on the internet, but that is a topic for a later section.

@@

In the same vein as a VPN is Tor. Tor is a service that allows users to browse the
internet without anyone but themselves knowing both the source and destination of a
connection. Unlike a VPN, there is no central company that can see who is connecting to
what destination; the only person who knows that is the one using the service. The Tor
Project writes, \textcquote{tor:about}[.]{%
  \textins*{t}he goal of onion routing was to have a way to use the internet with
  as much privacy as possible, and the idea was to route traffic through
  multiple servers and encrypt it each step of the way%
} Tor not only provides privacy, it gives users total anonymity. Similar to
using a VPN, connecting to the Tor network before browsing the internet makes it
near impossible for observers to see what sites someone is accessing and for the
site to see where the request is coming from.  The potential applications for
near-perfect anonymity on the internet are innumerable. Those living under
oppressive governments can bypass censorship to reach the truth and Christians
can anonymously access the Bible online in restrictive countries, just to name a
few.

@@

\subsubsection{Malware}
The intersection of trust and computing is not a new topic.
\citeauthor{thompson:trust}, the creator of the Unix operating system, made this
the topic of his Turing Award lecture. In his lecture, he poses the question,
\textcquote[761]{thompson:trust}[.]{%
  to what extent should one trust a statement that
  a program is free of Trojan Horses? Perhaps it is more important to trust the
  people who wrote the software%
} With piracy, however, we add an additional actor in this chain of trust.
\citeauthor{thompson:trust} focuses solely on the developer-to-user relationship
of trust, with the assumption of an open-source project.
\citeauthor{thompson:trust}, thus, comments on how
\textcquote[763]{thompson:trust}{%
  \textins*{s}uch blatant code would not go undetected for long. Even the most
  casual perusal of the source of the C compiler would raise suspicions%
} When piracy is the method of distribution, however, the assumption of
equality between the source code and the delivered software does not hold. The
pirated software may have been tampered with, and the user has no simple way to
detect changes in the file(s) without doing some (often) complicated forensic
work. Although anti-malware tools may mitigate these issues, the problem of
trust still holds, and the anti-malware tools are not perfect. The character of
the seeder must be questioned, and it already stands on shaky ground if the
legality of their actions speaks for their moral compass and trustworthiness.
